---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(quanteda)
library(dplyr)
library(tidyverse)
library(utf8)
library(ggplot2)
setwd("C:/Users/sebah/Desktop/U/mineria de datos/ayudantia 2")
primer_tiempo2020 <- read_csv("Primer_Tiempo2020.csv", col_names = TRUE)
#str(primer_tiempo2020)
attach(primer_tiempo2020)
summary(primer_tiempo2020)


## Borrar Datos Char

primer_tiempo2020
primer_tiempo2020 <- primer_tiempo2020[,!(colnames(primer_tiempo2020) %in% c("id_partido", "fasepartido", "local", "tiempo","formationUsed", "torneo"))]
primer_tiempo2020


## Analisis descriptivo


fh2020 <- primer_tiempo2020[order(primer_tiempo2020$saves, decreasing = TRUE),]
fh2020

## Sub DataFrames


fh2020_rendimiento = fh2020[,colnames(primer_tiempo2020) %in% c("equipo", "partido", "saves", "possessionPercentage", "precision_rendimiento")]
fh2020_rendimiento = fh2020_rendimiento[order(fh2020_rendimiento$possessionPercentage, decreasing = TRUE),]
fh2020_rendimiento
fh2020_fauls <- NULL
fh2020_fauls = fh2020[,colnames(primer_tiempo2020) %in% c("equipo", "partido", "totalTackle", "totalYellowCard", "fkFoulWon", "fkFoulLost", "totalOffside", "totalRedCard")]
fh2020_fauls = fh2020_fauls[order(fh2020_fauls$totalYellowCard, decreasing = TRUE),]
fh2020_fauls


## Filtrar Datos

everton <- filter(primer_tiempo2020, equipo == "Everton")
everton_rendimiento <- filter(fh2020_rendimiento, equipo == "Everton")
everton_fauls <- filter(fh2020_fauls, equipo == "Everton")


## Agregar Promedio/Suma Total/Min/...

everton_rendimiento <- everton_rendimiento[,!(colnames(everton_rendimiento) %in% c("equipo"))] 
Promedios_rend <- c("Promedio rendimiento",mean(everton_rendimiento$saves),mean(everton_rendimiento$possessionPercentage),mean(everton_rendimiento$precision_pases))
everton_rendimiento <- rbind(everton_rendimiento, Promedios_rend)
Max_rend <- c("Max rendimiento",max(everton_rendimiento$saves),max(everton_rendimiento$possessionPercentage),max(everton_rendimiento$precision_pases))
everton_rendimiento <- rbind(everton_rendimiento, Max_rend)
Min_rend <- c("Min rendimiento",min(everton_rendimiento$saves),min(everton_rendimiento$possessionPercentage),min(everton_rendimiento$precision_pases))
everton_rendimiento <- rbind(everton_rendimiento, Min_rend)
everton_rendimiento


## Graficos

rendimiento_everton <- everton$saves
everton2 <- everton[order(everton$saves, decreasing = FALSE),]
dotchart(everton$goals, labels = everton$partido, cex=0.5, xlab = "goles", ylab = "Partido")
dotchart(everton$totalPass, labels = utf8_encode(everton$partido), cex=0.5, xlab = "pases", ylab = "Partido")
dotchart(everton$accuratePass, labels = utf8_encode(everton$partido), cex=0.5, xlab = "rendimiento", ylab = "Partido")
dotchart(everton2$totalPass, labels = utf8_encode(everton$partido), cex=0.5, xlab = "rendimiento", ylab = "Partido")
dotchart(everton2$totalPass, labels = utf8_encode(everton$partido), main="rendimiento Acertados everton", pch = 16, col=c("darkblue","dodgerblue"),lcolor="gray90", cex=0.8, xlab = "rendimiento", ylab = "Partido", cex.main=2,cex.lab=1.5)


## Analisis de Texto

texto <- primer_tiempo2020$partido
texto <- char_tolower(texto)
texto <- iconv(texto, to = "ASCII//TRANSLIT")
a <- dfm(texto, remove = c(stopwords("es"), "vs", "Universidad"))
dim(a)